Powdery mildew yield loss mitigation strategies in mungbean, a meta-analysis.

### 2020-06-19 03_Prep_data.Rmd
Typos and some words for clarification

First lets get a list the of trials that reported LSD.  
```{r all_LSD_trials}
Trials <- PM_MB_means %>%
   filter(Y_error_type == "lsd (P=0.05)") %>%
   select(trial_ref) %>%
   distinct()
```

@@

```{r LSD_2_Sampling Variance}

@@

We may want to consider rowspacing in the trials, However one of the locations has NA as the row spacing. 
Fow now lets assign the most used row spacing of 0.33
```{r}
slimmer_PM_dat[is.na(slimmer_PM_dat$row_spacing),]
slimmer_PM_dat[is.na(slimmer_PM_dat$row_spacing),"row_spacing"] <- 0.33

>>>>

First lets get a list the of trials that reported LSD.  
```{r all_LSD_trials}
Trials <- PM_MB_means %>%
   filter(Y_error_type == "lsd (P=0.05)") %>%
   select(trial_ref) %>%
   distinct()
Trials
```
Lets use this list of trials to subset the data and calculate sampling variances.

@@

```{r LSD_2_Sampling_Variance}

@@

We may want to consider row spacing in the trials, However one of the locations has NA as the row spacing. 
Fow now lets assign the most used row spacing of 0.33
```{r}
slimmer_PM_dat[is.na(slimmer_PM_dat$row_spacing),]
slimmer_PM_dat[is.na(slimmer_PM_dat$row_spacing),"row_spacing"] <- 0.33
